Assessment of referee comment regarding q value and zero assumption

### 2016-09-28 analysis/adaptive_shrinkage.Rmd
update

```{r plotting}
make_df_for_ashplot = function(sim1,sim2,ash1,ash2,name1="spiky",name2="big-normal"){
  df = data.frame(betahat = c(sim1$input$betahat,sim2$input$betahat),
                beta_est = c(ash1$PosteriorMean, ash2$PosteriorMean),
                lfsr = c(ash1$lfsr, ash2$lfsr),
                s=c(sim1$input$sebetahat,sim2$input$sebetahat),
                scenario=c(rep(name1,NSAMP),rep(name2,NSAMP)))
  df$signif = df$lfsr<0.05
  return(df)
}

@@

Let's see how these are affected by changing the modelling assumptions so that
the standardized beta are exchangeable (rather than the beta being exchangeable).
```{r run-ash-ET}
beta.bignormal.ash.ET = ash(sim.bignormal$input$betahat, s,model="ET",mixcompdist="normal")
beta.spiky.ash.ET = ash(sim.spiky$input$betahat, s,model="ET",mixcompdist="normal")
df.ET = make_df_for_ashplot(sim.spiky,sim.bignormal,beta.spiky.ash.ET,beta.bignormal.ash.ET)
ashplot(df.ET,ylab="Shrunken beta estimate (ET model)")
pval_plot(df.ET)
```

>>>>

```{r plotting}
make_df_for_ashplot = function(sim1,sim2,ash1,ash2,name1="spiky",name2="big-normal"){
  df = data.frame(betahat = c(sim1$input$betahat,sim2$input$betahat),
                beta_est = c(get_pm(ash1), get_pm(ash2)),
                lfsr = c(get_lfsr(ash1), get_lfsr(ash2)),
                s=c(sim1$input$sebetahat,sim2$input$sebetahat),
                scenario=c(rep(name1,NSAMP),rep(name2,NSAMP)))
  df$signif = df$lfsr<0.05
  return(df)
}

@@

Let's see how these are affected by changing the modelling assumptions so that
the standardized beta are exchangeable (rather than the beta being exchangeable).
```{r run-ash-ET}
beta.bignormal.ash.ET = ash(sim.bignormal$input$betahat, s,alpha=1,mixcompdist="normal")
beta.spiky.ash.ET = ash(sim.spiky$input$betahat, s,alpha=1,mixcompdist="normal")
df.ET = make_df_for_ashplot(sim.spiky,sim.bignormal,beta.spiky.ash.ET,beta.bignormal.ash.ET)
ashplot(df.ET,ylab="Shrunken beta estimate (ET model)")
pval_plot(df.ET)
```

### 2016-09-28 analysis/efron.fcr.Rmd
update example
update

Here we can see how the partition of $z$ scores compares with the truth. Note the effect of the unimodal assumption is to extend the inferred alternative distribution toward 0.
```{r}
  source("../R/nullalthist.R")
  par(mfcol=c(2,1))
  nullalthist(z,lfdr=res.ash.true$lfdr,main="true partition")
  nullalthist(z,lfdr=res.ash$lfdr,main="inferred partition")
```

Comparing the inferred Posterior Means, lfdr, and lfsr with the true values of these quantities, we find reassuringly good correspondence.
```{r}
  par(mfcol=c(1,1))
  plot(res.ash.true$PosteriorMean,res.ash$PosteriorMean,xlab="Truth", ylab="ash.hu",main="Posterior Mean (inferred vs truth)",xlim=c(-6,1),ylim=c(-6,1))
  abline(a=0,b=1,col=2,lwd=3)

    plot(res.ash.true$lfdr,res.ash$lfdr,xlab="Truth", ylab="ash.hu",main="lfdr (inferred vs truth)",xlim=c(0,1),ylim=c(0,1))
  abline(a=0,b=1,col=2,lwd=3)

  plot(res.ash.true$lfsr,res.ash$lfsr,xlab="Truth", ylab="ash.hu",main="lfsr (inferred vs truth)",xlim=c(0,1),ylim=c(0,1))
  abline(a=0,b=1,col=2,lwd=3)

@@

@@

par(mfrow=c(1,3))
plot(res.ash.true$lfdr,res.ash$lfdr,xlab="Truth (lfdr)", ylab="ash.hu",main="ash.hu",xlim=c(0,1),ylim=c(0,1))
abline(a=0,b=1,col=2,lwd=3)
plot(res.ash.true$lfdr,res.locfdr$fdr,xlab="Truth (lfdr)", ylab="Estimate",main="locfdr",xlim=c(0,1),ylim=c(0,1))
abline(a=0,b=1,col=2,lwd=3)
plot(res.ash.true$lfdr,res.qvalue$lfdr,xlab="Truth (lfdr)", ylab="Estimate",main="qvalue",xlim=c(0,1),ylim=c(0,1))
abline(a=0,b=1,col=2,lwd=3)

@@

The following plot compares the (symmetric-tail) 95% CIs from ash (red) for the "significant" observations with Bayes rule (green), similar to Figure 8 from Efron. Note that the lower 97.5% point is pretty accurate, but the upper 97.5% point is curtailed - presumably due, at least in part, to the short tails of the uniform mixture.
```{r}
  CImatrix= ashr::ashci(res.ash,level=0.95)
  BayesComparePlot=function(CImatrix,altmean=-3,...){
    plot(z,mu,xlim=c(-8,0),...)
    points(z[CImatrix[,1]],CImatrix[,5],col="red")
    points(z[CImatrix[,1]],CImatrix[,4],col="red")

>>>>

Here we can see how the partition of $z$ scores compares with the truth. Note the effect of the unimodal assumption is to extend the inferred alternative distribution toward 0.
```{r}
  source("../R/nullalthist.R")
  par(mfcol=c(2,1))
  nullalthist(z,lfdr=ashr::get_lfdr(res.ash.true),main="true partition")
  nullalthist(z,lfdr=ashr::get_lfdr(res.ash),main="inferred partition")
```

Comparing the inferred Posterior Means, lfdr, and lfsr with the true values of these quantities, we find reassuringly good correspondence.
```{r}
  par(mfcol=c(1,1))
  plot(ashr::get_pm(res.ash.true),ashr::get_pm(res.ash),xlab="Truth", ylab="ash.hu",main="Posterior Mean (inferred vs truth)",xlim=c(-6,1),ylim=c(-6,1))
  abline(a=0,b=1,col=2,lwd=3)

    plot(ashr::get_lfdr(res.ash.true),ashr::get_lfdr(res.ash),xlab="Truth", ylab="ash.hu",main="lfdr (inferred vs truth)",xlim=c(0,1),ylim=c(0,1))
  abline(a=0,b=1,col=2,lwd=3)

  plot(ashr::get_lfsr(res.ash.true),ashr::get_lfsr(res.ash),xlab="Truth", ylab="ash.hu",main="lfsr (inferred vs truth)",xlim=c(0,1),ylim=c(0,1))
  abline(a=0,b=1,col=2,lwd=3)

@@

# Comparison with qvalue and locfdr

@@

par(mfrow=c(1,3))
plot(ashr::get_lfdr(res.ash.true),ashr::get_lfdr(res.ash),xlab="Truth (lfdr)", ylab="ash.hu",main="ash.hu",xlim=c(0,1),ylim=c(0,1))
abline(a=0,b=1,col=2,lwd=3)
plot(ashr::get_lfdr(res.ash.true),res.locfdr$fdr,xlab="Truth (lfdr)", ylab="Estimate",main="locfdr",xlim=c(0,1),ylim=c(0,1))
abline(a=0,b=1,col=2,lwd=3)
plot(ashr::get_lfdr(res.ash.true),res.qvalue$lfdr,xlab="Truth (lfdr)", ylab="Estimate",main="qvalue",xlim=c(0,1),ylim=c(0,1))
abline(a=0,b=1,col=2,lwd=3)

@@

The following plot compares the (symmetric-tail) 95% CIs from ash (red) for the "significant" observations with Bayes rule (green), similar to Figure 8 from Efron. Note that the lower 97.5% point is pretty accurate, but the upper 97.5% point is curtailed - presumably due, at least in part, to the short tails of the uniform mixture.
```{r}
  CImatrix= ashr::ashci(res.ash,level=0.95)
  BayesComparePlot=function(CImatrix,altmean=-3,...){
    plot(z,mu,xlim=c(-8,0),...)
    points(z,CImatrix[,1],col="red")
    points(z,CImatrix[,2],col="red")

### 2016-09-28 analysis/estimate_mode.Rmd
update

```{r}

check_mode = function(betahat, sebetahat,mixcompdist){
    z.ash=ashr::ash(betahat,sebetahat,mixcompdist=mixcompdist,nonzeromode=TRUE)
    average.posteriormean = mean(z.ash$PosteriorMean)
    fitted.mode = ashr::comp_mean(z.ash$fitted.g)[1]

    z.ash1 = ashr::ash(betahat-fitted.mode,sebetahat, mixcompdist=mixcompdist) #refit to get g
    g = z.ash1$fitted.g
    loglik = z.ash1$loglik

    loglik.down = ashr::ash(z-fitted.mode-0.01,1,g=g)$loglik
    loglik.up  = ashr::ash(z-fitted.mode+0.01,1,g=g)$loglik
    loglik.posteriormean = ashr::ash(z-average.posteriormean,1,g=g)$loglik

@@

```{r}
  set.seed(100)
  beta = rexp(1000)
  betahat = beta + rnorm(1000,0,0.1)
  z.ash.hu = ashr::ash(betahat,0.1,mixcompdist="halfuniform",outputlevel=4,method="shrink")
  z.ash.pu = ashr::ash(betahat,0.1,mixcompdist="+uniform",outputlevel=4,method="shrink")

  z.ash.hu2 = ashr::ash(betahat-0.2,0.1,mixcompdist="halfuniform",outputlevel=4,method="shrink")
  z.ash.pu2 = ashr::ash(betahat-0.1,0.1,mixcompdist="+uniform",outputlevel=4,method="shrink")

  z.ash.hu.nzm = ashr::ash(betahat,0.1,mixcompdist="halfuniform",nonzeromode=TRUE,method="shrink")
  z.ash.hu$loglik
  z.ash.hu.nzm$loglik

  test.op = function(c){return(-ashr::ash(betahat-c,0.1,mixcompdist="halfuniform",outputlevel=4,method="shrink")$loglik)}
  optimize(test.op,interval=c(min(betahat),max(betahat)))
#  check_mode(betahat,.1,mixcompdist="halfuniform")
```

>>>>

```{r}
library(ashr)
check_mode = function(betahat, sebetahat,mixcompdist){
    z.ash=ash(betahat,sebetahat,mixcompdist=mixcompdist,mode="estimate")
    average.posteriormean = mean(get_pm(z.ash))
    fitted.mode = comp_mean(get_fitted_g(z.ash))[1]

    z.ash1 = ash(betahat-fitted.mode,sebetahat, mixcompdist=mixcompdist) #refit to get g
    g = get_fitted_g(z.ash1)
    loglik = get_loglik(z.ash1)

    loglik.down = ash(z-fitted.mode-0.01,1,g=g)$loglik
    loglik.up  = ash(z-fitted.mode+0.01,1,g=g)$loglik
    loglik.posteriormean = ash(z-average.posteriormean,1,g=g)$loglik

@@

```{r}
  set.seed(100)
  beta = rexp(1000)
  betahat = beta + rnorm(1000,0,0.1)
  z.ash.hu = ash(betahat,0.1,mixcompdist="halfuniform",outputlevel=4,method="shrink")
  z.ash.pu = ash(betahat,0.1,mixcompdist="+uniform",outputlevel=4,method="shrink")

  z.ash.hu2 = ash(betahat-0.2,0.1,mixcompdist="halfuniform",outputlevel=4,method="shrink")
  z.ash.pu2 = ash(betahat-0.1,0.1,mixcompdist="+uniform",outputlevel=4,method="shrink")

  z.ash.hu.nzm = ash(betahat,0.1,mixcompdist="halfuniform",mode="estimate",method="shrink")
  z.ash.hu$loglik
  z.ash.hu.nzm$loglik

#  check_mode(betahat,.1,mixcompdist="halfuniform")
```

### 2016-09-28 analysis/make_GOODPOOR_figs.Rmd
update

```{r GOODPOOReg_scatter, dev='pdf', fig.width=6.5, fig.height=3}
res = rbind(data.frame(x= res.qvalue.good$qvalues, y = res.qvalue$qvalues[GOOD],type="qvalue"),
            data.frame(x=res.locfdr.good$fdr,y=res.locfdr$fdr[GOOD],type='locfdr'), 
            data.frame(x=res.ash.good$lfsr,y=res.ash$lfsr[GOOD],type="ashr"))

@@

```{r lfsr_vs_pval_GOODPOOR, dev='pdf', fig.width=6.5, fig.height=3}
make_df_for_pval=function(ash,method="default"){
  df = data.frame(p=pnorm(-abs(ash$data$betahat/ash$data$sebetahat)),lfsr=ash$lfsr,s=ash$data$sebetahat,method=method)
}

@@

res.ash.ET = ash(betahat,sebetahat,method="fdr",model="ET",mixcompdist="normal",outputlevel=4)
p=plot_pval_vs_lfsr(rbind(
  make_df_for_pval(res.ash,method="Default prior (alpha=0)"),
  make_df_for_pval(res.ash.ET,method="p-value prior (alpha=1)")))
print(p+ theme(axis.text.x = element_text(size = 8,angle=45)) + 
        scale_colour_manual(values=c("blue","red")))

>>>>

```{r GOODPOOReg_scatter, dev='pdf', fig.width=6.5, fig.height=3}
res = rbind(data.frame(x= res.qvalue.good$qvalues, y = res.qvalue$qvalues[GOOD],type="qvalue"),
            data.frame(x=res.locfdr.good$fdr,y=res.locfdr$fdr[GOOD],type='locfdr'), 
            data.frame(x=get_lfsr(res.ash.good),y=get_lfsr(res.ash)[GOOD],type="ashr"))

@@

```{r lfsr_vs_pval_GOODPOOR, dev='pdf', fig.width=6.5, fig.height=3}
make_df_for_pval=function(ash,method="default"){
  df = data.frame(p=pnorm(-abs(ash$data$x/ash$data$s)),lfsr=get_lfsr(ash),s=ash$data$s,method=method)
}

@@

res.ash.ET = ash(betahat,sebetahat,method="fdr",alpha=1,mixcompdist="normal",outputlevel=4)
p=plot_pval_vs_lfsr(rbind(
  make_df_for_pval(res.ash,method="Default prior (alpha=0)"),
  make_df_for_pval(res.ash.ET,method="p-value prior (alpha=1)")))
print(p+ theme(axis.text.x = element_text(size = 8,angle=45)) + 
        scale_colour_manual(values=c("blue","red")))

### 2016-09-28 analysis/makefig_FDReg.Rmd
update

Here's an example of how qvalue decomposes $p$ values into null and alternative components
```{r}
#pdf("../figures/FDReg_hist.pdf",width=6,height=3)
par(mai=c(0.5,0.5,0.2,0.2),mgp = c(3, 0.5, 0))
layout(matrix(1:2,ncol=2,byrow=TRUE))
plot_FDReg_hist(pval,res.qvalue$pi0,type=1,title="p values",cex.axis=0.8,cex.main=0.8)
plot_FDReg_hist(pval,res.qvalue$pi0,type=4,cex.axis=0.8,yaxt='n',textsize=0.9,cex.main=0.8,title="Decomposition into null/alternative")
axis(side=2, labels=FALSE,tck=-0.01)
```

@@

#p value histograms
altnullhist(pval,qval_fdr,main="p values",ncz=50,xaxt='n',cex.axis=0.8)
#plot_FDReg_hist(pval,res.qvalue$pi0,type=2,title="p values",xaxt='n',cex.axis=0.8)
axis(side=1, labels=FALSE,tck=-0.01)
#mtext(side=3,"p values",line=1)
altnullhist(pval,res.locfdr$fdr,main="",ncz=50,xaxt='n',cex.axis=0.8)
axis(side=1, labels=FALSE,tck=-0.01)
altnullhist(pval,res.mixfdr$fdr,main="",ncz=50,xaxt='n',cex.axis=0.8)
axis(side=1, labels=FALSE,tck=-0.01)
altnullhist(pval,res.ash$lfdr,main="",ncz=50,xaxt='n',cex.axis=0.8)
axis(side=1, labels=TRUE,tck=-0.01,cex.axis=0.8)
#mtext(side=1,"p values",line=2)

#z score histograms
nullalthist(zscore,qval_fdr,main="z scores",ncz=50,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=FALSE,tck=-0.01)
#mtext(side=3,"z scores",line=1)
nullalthist(zscore,res.locfdr$fdr,main="",ncz=50,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=FALSE,tck=-0.01)
nullalthist(zscore,res.mixfdr$fdr,main="",ncz=50,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=FALSE,tck=-0.01)
nullalthist(zscore,res.ash$lfdr,main="",ncz=50,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=TRUE,tck=-0.01,cex.axis=0.8)
#mtext(side=1,"z scores",line=2)

@@

#p value histograms
altnullhist(pval,qval_fdr,main="p values: qvalue",ncz=ncz,xaxt='n',cex.axis=0.8)
#plot_FDReg_hist(pval,res.qvalue$pi0,type=2,title="p values",xaxt='n',cex.axis=0.8)
axis(side=1, labels=FALSE,tck=-0.01)
#mtext(side=3,"p values",line=1)
altnullhist(pval,res.locfdr$fdr,main="locfdr",ncz=ncz,xaxt='n',cex.axis=0.8)
axis(side=1, labels=FALSE,tck=-0.01)
altnullhist(pval,res.mixfdr$fdr,main="mixfdr",ncz=ncz,xaxt='n',cex.axis=0.8)
axis(side=1, labels=FALSE,tck=-0.01)
altnullhist(pval,res.ash$lfdr,main="ash",ncz=ncz,xaxt='n',cex.axis=0.8)
axis(side=1, labels=TRUE,tck=-0.01,cex.axis=0.8)
#mtext(side=1,"p values",line=2)

#z score histograms
nullalthist(zscore,qval_fdr,main="z scores: qvalue",ncz=ncz,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=FALSE,tck=-0.01)
#mtext(side=3,"z scores",line=1)
nullalthist(zscore,res.locfdr$fdr,main="locfdr",ncz=ncz,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=FALSE,tck=-0.01)
nullalthist(zscore,res.mixfdr$fdr,main="mixfdr",ncz=ncz,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=FALSE,tck=-0.01)
nullalthist(zscore,res.ash$lfdr,main="ash",ncz=ncz,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=TRUE,tck=-0.01,cex.axis=0.8)
#mtext(side=1,"z scores",line=2)

>>>>

Here's an example of how qvalue decomposes $p$ values into null and alternative components. First the $p$ values:
```{r}
#pdf("../figures/FDReg_hist.pdf",width=6,height=3)
#par(mai=c(0.5,0.5,0.2,0.2),mgp = c(3, 0.5, 0))
#layout(matrix(1:2,ncol=2,byrow=TRUE))
plot_FDReg_hist(pval,res.qvalue$pi0,type=1,title="p values",cex.axis=0.8,cex.main=0.8)

Now the decomposition:
```{r}
plot_FDReg_hist(pval,res.qvalue$pi0,type=4,cex.axis=0.8,yaxt='n',textsize=0.9,cex.main=0.8,title="Decomposition into null/alternative")
axis(side=2, labels=FALSE,tck=-0.01)
```

@@

#p value histograms
altnullhist(pval,qval_fdr,main="p values",ncz=50,xaxt='n',cex.axis=0.8)
#plot_FDReg_hist(pval,res.qvalue$pi0,type=2,title="p values",xaxt='n',cex.axis=0.8)
axis(side=1, labels=FALSE,tck=-0.01)
#mtext(side=3,"p values",line=1)
altnullhist(pval,res.locfdr$fdr,main="",ncz=50,xaxt='n',cex.axis=0.8)
axis(side=1, labels=FALSE,tck=-0.01)
altnullhist(pval,res.mixfdr$fdr,main="",ncz=50,xaxt='n',cex.axis=0.8)
axis(side=1, labels=FALSE,tck=-0.01)
altnullhist(pval,get_lfdr(res.ash),main="",ncz=50,xaxt='n',cex.axis=0.8)
axis(side=1, labels=TRUE,tck=-0.01,cex.axis=0.8)
#mtext(side=1,"p values",line=2)

#z score histograms
nullalthist(zscore,qval_fdr,main="z scores",ncz=50,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=FALSE,tck=-0.01)
#mtext(side=3,"z scores",line=1)
nullalthist(zscore,res.locfdr$fdr,main="",ncz=50,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=FALSE,tck=-0.01)
nullalthist(zscore,res.mixfdr$fdr,main="",ncz=50,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=FALSE,tck=-0.01)
nullalthist(zscore,get_lfdr(res.ash),main="",ncz=50,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=TRUE,tck=-0.01,cex.axis=0.8)
#mtext(side=1,"z scores",line=2)

@@

#p value histograms
altnullhist(pval,qval_fdr,main="p values: qvalue",ncz=ncz,xaxt='n',cex.axis=0.8)
#plot_FDReg_hist(pval,res.qvalue$pi0,type=2,title="p values",xaxt='n',cex.axis=0.8)
axis(side=1, labels=FALSE,tck=-0.01)
#mtext(side=3,"p values",line=1)
altnullhist(pval,res.locfdr$fdr,main="locfdr",ncz=ncz,xaxt='n',cex.axis=0.8)
axis(side=1, labels=FALSE,tck=-0.01)
altnullhist(pval,res.mixfdr$fdr,main="mixfdr",ncz=ncz,xaxt='n',cex.axis=0.8)
axis(side=1, labels=FALSE,tck=-0.01)
altnullhist(pval,get_lfdr(res.ash),main="ash",ncz=ncz,xaxt='n',cex.axis=0.8)
axis(side=1, labels=TRUE,tck=-0.01,cex.axis=0.8)
#mtext(side=1,"p values",line=2)

#z score histograms
nullalthist(zscore,qval_fdr,main="z scores: qvalue",ncz=ncz,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=FALSE,tck=-0.01)
#mtext(side=3,"z scores",line=1)
nullalthist(zscore,res.locfdr$fdr,main="locfdr",ncz=ncz,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=FALSE,tck=-0.01)
nullalthist(zscore,res.mixfdr$fdr,main="mixfdr",ncz=ncz,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=FALSE,tck=-0.01)
nullalthist(zscore,get_lfdr(res.ash),main="ash",ncz=ncz,xaxt='n',cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6))
axis(side=1, labels=TRUE,tck=-0.01,cex.axis=0.8)
#mtext(side=1,"z scores",line=2)

### 2016-09-28 analysis/referee_uaza.Rmd
update

For comparison here is the decomposition, using ash, of $z$ scores into null and alternative components.
```{r}
lfdr.ash=ashr::ash(x.est,1/sqrt(30))$lfdr
nullalthist(zscore,lfdr.ash,main="ash partition of z \n into null and alternative",ncz=60,cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6),xlab="z score")
```

For completeness here is (roughly) the ``true" decomposition of $z$ scores into null and alternative components.
```{r}
trueg = ashr::normalmix(c(0.8,0.2),c(0,0),c(0,1))
lfdr.true=ashr::ash(x.est,1/sqrt(30),g=trueg,fixg=TRUE)$lfdr
nullalthist(zscore,lfdr.true,main="true partition of z \n into null and alternative",ncz=60,cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6),xlab="z score")
```

>>>>

For comparison here is the decomposition, using ash, of $z$ scores into null and alternative components.
```{r}
library(ashr)
lfdr.ash=get_lfdr(ash(x.est,1/sqrt(30)))
nullalthist(zscore,lfdr.ash,main="ash partition of z \n into null and alternative",ncz=60,cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6),xlab="z score")
```

For completeness here is (roughly) the ``true" decomposition of $z$ scores into null and alternative components.
```{r}
trueg = ashr::normalmix(c(0.8,0.2),c(0,0),c(0,1))
lfdr.true=get_lfdr(ash(x.est,1/sqrt(30),g=trueg,fixg=TRUE))
nullalthist(zscore,lfdr.true,main="true partition of z \n into null and alternative",ncz=60,cex.axis=0.8,ylim=c(0,0.3),xlim=c(-6,6),xlab="z score")
```
